Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2016-11-11 longSC.tex
adopt the final comment from You, version for IRC R1

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are merged quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results. The various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
The strength of SC$(m,n)$ correlation becomes larger as the minimum $p_{\rm T}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
This $p_{\rm T}$ dependence correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or $p_{\rm T}$ increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Hence the Glauber initial condition with $\eta/s=0.20$ can be ruled out. We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.

@@

Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), neither of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest. The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.

>>>>

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherSC.eps}}
                       \resizebox{0.48\textwidth}{!}{\includegraphics{figs/fig2_QConly_higherNSC.eps}}
        \caption{The result of SC($m$,$n$) (left figure) and NSC($m$,$n$) (right figure) with flow harmonic order up to $5^{\mathrm{th}}$ in $\PbPb$ collisions at $\snn=2.76$~TeV. The lower order harmonic correlations (SC(3,2), SC(4,2), NSC(3,2) and NSC(4,2)) are taken from the recent publication~\cite{ALICE:2016kpq} and shown as bands. Note that the systematic and statistical errors are combined quadratically for these lower order harmonic correlations  and SC(4,2) and SC(3,2) on the left figure are scaled down by factor of 10.}
        \label{fig:Figure_1}
              \end{center}
\end{figure*}

@@

To obtain the $p_{\rm T}$ dependence of SC$(m,n)$ results, we vary minimum $p_{\rm T}$ cuts, instead of $p_{\rm T}$ bin-by-bin interval, in order to avoid large statistical fluctuations in the results. Various minimum $p_{\rm T}$ cuts from 0.2 to 1.5~GeV/$c$ are applied.
The results of $p_{\rm T}$ dependence SC(3,2) and SC(4,2) with minimum $p_{\rm T}$ cuts, $0.2<p_{\rm T}<0.7$~GeV/$c$, are shown on the left top in Fig.~\ref{fig:Figure_2}.
The strength of SC$(m,n)$ becomes larger as the minimum $p_{\rm T}$ increases. 
%This indicates that the relationship between event-by-event fluctuations of two different flow harmonics $v_m$ and $v_n$ is stronger for high $p_{\rm T}$ particles. 
This $p_{\rm T}$ dependent correlations have much stronger centrality dependence, where SC$(m,n)$ gets much larger as the centrality or the minimum $p_{\rm T}$ cut increase. 
NSC(3,2) and NSC(4,2) with different minimum cuts are shown on the right in Fig.~\ref{fig:Figure_2}.
The strong $p_{\rm T}$ dependence observed in SC$(m,n)$ is not clearly seen in NSC$(m,n)$. NSC$(m,n)$ results are aligned all together and consistent in errors for all minimum $p_{\rm T}$ cuts. 
This may indicate that the $p_{\rm T}$ dependence of SC$(m,n)$ does not solely result from the correlation between flow harmonics but results from the $p_{\rm T}$  dependent individual $v_n$ values. 
The minimum $p_{\rm T}$ cuts are extended from 0.8  to 1.5~GeV/$c$ and the results are shown on the bottom panels in Fig.~\ref{fig:Figure_2}.
As for SC$(m,n)$, the similar trends are observed as for $p_{\rm T}<0.8$~GeV/$c$, however NSC$(m,n)$ tends to decrease as the minimum $p_{\rm T}$ or the centrality increase.
The $p_{\rm T}$ dependence for NSC(3,2) is not clearly seen and it is consistent with no $p_{\rm T}$ dependence within the current statistical and systematic errors for the centrality range $<$30\% and shows moderate decreasing trend for increasing $p_{\rm T}$ for $>$30\% centrality range.
NSC(4,2) shows a moderate decreasing trend as $p_{\rm T}$ or the centrality increase. These observations are strikingly different from $p_{\rm T}$ dependence of individual flow harmonics, where the relative flow fluctuations $\sigma_{v_2}/\langle v_{2} \rangle$~\cite{Voloshin:2008dg} are independent of momentum up to $p_{\rm T}$ $\sim$ 8~GeV/$c$ (see Fig. 3 in Ref.~\cite{Abelev:2012di}).
%(see further discussions in Sec.~\ref{sec:ptdepsc})
%This might be an indication of possible viscous corrections for the equilibrium distribution at hadronic freeze-out~\cite{Luzum:2010ad}.
%However within the current statistical and systematic errors, it is consistent with no $p_{\rm T}$ dependence of NSC$(m,n)$ (see further discussions in Sec.~\ref{sec:ptdepsc}).

@@

The results with the comparison to VISH2+1 calculation~\cite{Zhu:2016puf} are shown in Fig.~\ref{fig:Figure_3}.  All the models with large $\eta/s$ regardless of the initial conditions ($\eta/s=0.2$ for MC-KLN and MC-Glauber initial conditions and $\eta/s=0.16$ for AMPT initial condition) fail to capture the centrality dependence of SC(3,2) and SC(4,2). 
On the other hand, among the models with small $\eta/s$ ($\eta/s=0.08$), the one with the AMPT initial condition describes the data better both for SC(3,2) and SC(4,2) in general but it cannot describe the data quantitively for most of the centrality ranges.
Similarly as the above mentioned hydrodynamic calculations~\cite{Niemi:2015qia}, the sign of the normalized NSC(3,2) in these models is opposite to its signature in the data in 0-10\% central collisions. NSC(3,2) does not show sensitivity to initial conditions nor to different $\eta/s$ parameterizations and cannot be described by these models quantitively.
However NSC(4,2) is sensitive both to initial conditions and $\eta/s$ parameterizations.
Even though NSC(4,2) favors both AMPT initial condition with $\eta/s=0.08$ and MC-Glauber initial condition with $\eta/s=0.20$,
SC(4,2) can be only described by smaller $\eta/s$ from AMPT and MC-Glauber initial conditions. Hence the MC-Glauber initial condition with $\eta/s=0.20$ can be ruled out. We come to a conclusion based on the tested model parameters that $\eta/s$ should be small and AMPT initial condition is favored by the data.

@@

Finally, the extracted results for final state particles from AMPT simulations in the same way as for the data are compared in Fig.~\ref{fig:Figure_4}.
As for SC(3,2), none of the settings can describe the data and the setting with the default AMPT model somewhat follows the trend of the data closest. The same setting can describe NSC(3,2) fairly well and also the sign of NSC(3,2) is well reproduced by this setting while all the hydrodynamic calculations in this article failed to describe the sign of the observable in the most central collisions.
Interestingly the string melting AMPT model cannot capture the data well where the strength of the correlation is weaker than the default model.
The third version based on the string melting configuration with the hadronic rescattering phase off is also shown to quantify its influence.
This late hadronic rescattering stage makes both SC(3,2) and NSC(3,2) stronger in the string melting AMPT model but it is not enough to describe the data.
Further we investigated why the default AMPT model can describe NSC(3,2) fairly well but underestimates SC(3,2). By taking the differences in the individual flow harmonics ($v_2$ and $v_3$) between the model and data into account, we were able to recover the difference in SC(3,2) between the data and the model. The discrepancy in SC(3,2) can be explained by the overestimated individual $v_n$ values reported in \cite{Adam:2016nfo} in all the centrality ranges.
